Manuscript draft

### 2019-07-17 manuscript/manuscript draft.Rmd
updated manuscript draft

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivariate_models <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/multivariate_models.csv", stringsAsFactors = FALSE, check.names = FALSE)

kable(multivariate_models, format = "latex", booktabs = TRUE, caption = "Multivariate model summary", escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1:10, width = "2cm") %>%
  add_header_above(c(" ", " ", "Climate variables" = 7, " "))

```
